The Effects of the 2023 Rule Changes in Major League Baseball

### 2023-10-30 manuscript/paper.tex
added outline for rest of paper

>>>>

\section{Literature Review}
\label{sec:lit}

Examine relevant works.

\section{Data}
\label{sec:data}

Use this section to describe the data that helps to answer your research
questions.

\section{Methods}
\label{sec:meth}

Use this section to present the methodologies that will generate results by
analyzing the data.

\section{Results}
\label{sec:resu}

Summarize the results.

\section{Discussion}
\label{sec:disc}

What are the main contributions again?

What are the limitations of this study?

What are worth pursuing further in the future?
